---
title: "IMS3.3"
author: "Ariana Kim"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    fig_width: 10
    fig_height: 6
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(tidyverse)
library(stringr)
library(knitr)
library(ggplot2)
library(showtext)
library(devtools)



```

# Background

## Research Question
Can correcting be used as a friendship cue within children? 

## Study Design 
Between-Subjects Design 

**Predictors:**
1. Reported Age in Years: 4 to 12

2. Public vs. Private Selections: 0=public-1=private
  + Categorical
  
3. Correcting vs. Affirmation:1=affirming, 2=correcting
  + Categorical 
  
**Outcome:**
1. Friend Choice: Jayden or Taylor

## Predicted Results 
We predict that children would think the main character is better friends with the character corrected in private, and better friends with the person affirmed in public. 

# Data Preparation 

## Load Data 
```{r recode}
data<-read.csv("IMS3.3/IMS3.3 (Pre-Reg) Data - Sheet1.csv") 


```
## Rename Variables 
```{r RV}
colnames(data)[6]<-"condition"

colnames(data)[8]<-"corrected_in_public"

colnames(data)[9]<-"corrected_in_private"

colnames(data)[17]<-"friendship_choice"

colnames(data)[23]<-"age"

data<-subset(data,data$condition %in% c("R","W"))

data<-subset(data,data$age>=4)
data<-subset(data,data$age<13)

data <- data %>%
  filter(data$Exclude. == "No")
```
# Data Analysis 
```{r DP}
data$choice<-(ifelse(data$friendship_choice==data$corrected_in_public, 0,1))

# Output Linear Regression 

choiceIMS3.3<-glm(choice~condition*age,
                  data=data, family="binomial")

summary(choiceIMS3.3)

plot<-ggplot(data=data,
              aes(x=age,
                  y=choice,
                  color=condition))+
  labs(x="Participant Age",
       y="Probability of Choosing Private",
       color="Condition")+
  geom_jitter(alpha=.2,height=.1)+
  geom_smooth(method="gam")+
  scale_color_manual(values=c("deepskyblue","violetred4"),labels=c("Correcting","Affirming"))+
  theme_gray(base_size=20)+
  geom_hline(yintercept=.5,linetype="dashed")+
  scale_x_continuous(breaks=4:12)

plot

```

## Analysis and Inferences 

As the age demographic increases, the purple regression line showcases that children believed Alex was better friends with the character corrected in private. 

As the age demographic increases, the blue regression line showcases that children believed Alex was better friends with the character affirmed in public. 

As we can see, our hypothesis was supported. Children thought Alex would be better friends with the person corrected in private, and better friends with the person affirmed in public. 




